Comparing the perfomance impacts of narrow and extended feature spaces in machine learning bots in the game of Schnapsen

### 2018-02-01 Text/paper.tex
Finished paper!!!

\title{The benefits of an extended feature space in a machine learning bot for the game Schnapsen}
\date{January 25, 2018}
\author{Lucas Faijdherbe, Daan Schrage and Ruben van der Ham\\\\
	\small Intelligent Systems\\
	\small Vrije Universiteit Amsterdam}

@@

\begin{abstract}
This paper examines the effect of extended and narrowed feature spaces on logistic regression machine learning bot. To illustrate this, 5 different machine learning bots were created: two bots with narrowed feature spaces, three bots with extended feature spaces. These bots were trained multiple times, and played multiple tournaments against multiple other bots. The results are.. 
\end{abstract}

@@

\clearpage
\section{Research Question}
In our research, we want to find \textit{what feature set will improve the machine learning bot's performance the most in the game of Schnapsen}. With improve the most, we mean as seen from the baseline. There is already a machine learning bot present, which will act as this base line. This bot has, what we will call the \textit{default feature space}- provided by the framework.  \\

>>>>

\title{Comparing the perfomance impacts of narrow and extended feature spaces in machine learning bots in the game of Schnapsen}
\date{January 25, 2018}
\author{Lucas Faijdherbe, Daan Schrage and Ruben van der Ham\\\\
	\small Intelligent Systems\\
	\small Vrije Universiteit Amsterdam}

@@

\begin{abstract}
This paper examines the effect of extended and narrowed feature spaces on logistic regression machine learning bot. To illustrate this, 5 different machine learning bots were created: two bots with narrowed feature spaces, three bots with extended feature spaces. These bots were trained multiple times, and played multiple tournaments against multiple other bots. The results were analyzed using statistics, but they did not show a substantial improvement or decrease of performance. There seems to be a small performance increase against specific bots, but no significant overall increase. We concluded that we need more extensive research to gain insight in performance of the different feature spaces.
\end{abstract}

@@

\clearpage
\section{Research Question}
In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance the most in the game of Schnapsen}. With improve the most, we mean as seen from the baseline. There is already a machine learning bot present, which will act as this base line. This bot has, what we will call the \textit{default feature space}- provided by the framework.  \\
